Stack Safety is a Security Property

### 2021-04-14 tex/main.tex
Filled in section 5

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
    \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

@@

An initial context \(\context_0 = \domMap_0, []\) where \(\domMap_0\) maps
the stack to \(\unsealed\) and all other addresses and all registers to \(\outside\).
Then at each step we update the context according to the context-step function,
\(\stepsto_C\). We will define this in terms of the operations
\(\push{\domMap}{\depth}{\components}\), in which \(\depth \in \mathbb{Z}\) and
\(\components \subseteq \COMPONENTS\), and \(\pop{\domMap}{\depth}\), pronounced
``push'' and ``pop'' and defined as follows.

\[
(\push{\domMap}{\depth}{\components}) ~ \component =
\begin{cases}
  \sealed{\depth} & \text{if } \domMap ~ \component = \unsealed
                    \text{ and } \component \in \components \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]
\[
(\pop{\domMap}{\depth}) ~ \component =
\begin{cases}
  \unsealed & \text{if } \domMap ~ \component = \sealed{\depth'} \text{ where }
              \depth' >= \depth\\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]
%
Push seals a set of components with its depth argument, and pop unseals all components
that were as deep as its argument or deeper.

Now we can define the context update relation. Let \(\sealcon\) be the sealing convention
that maps a machine state to a set of components, typically the set of addresses below
the stack pointer. Similarly, \(\retcon ~ \mach ~ \mach'\) will be the return convention
that relates the call state \(\mach\) to return states \(\mach'\) that are valid returns.
The usual return convention is that \(\mach\) and \(\mach'\) agree on the stack pointer,
and \(\mach'\) has its program counter advanced by one instruction from \(\mach\).

The call rule pushes the components sealed by the sealing convention with the depth
of the current caller, and determines the return target by partially applying the
return convention to the machine state, and pushes that onto the targets stack.
The return rule checks whether the attempted return actually manages to reach a
return target, traversing down the stack until the first one it finds. Recall that
we are not discussing well-bracketed control flow, so the return might skip over
a waiting caller. When a target is reached, {\em all} sealed components at or above
its depth are unsealed by the pop operation. If no target is reached, nothing is
popped at all. These rules are given inductively, and apply in the listed order.

\judgmenttwo[Call]
            {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
            {\(\depth = |\rts|\)}
            {\(\mach,(\domMap,\rts) \stepsto_C
              \push{\domMap}{\depth}{\sealcon ~ \mach},(\retcon ~ \mach)::\rts\)}

\judgmentthree[ReturnFound]
              {\(\codemap ~ (\mach ~ \PCname) = \retmap\)}
              {\(\mach \stepsto \mach' \in \target\)}
              {\(\depth = |\rts|\)}
              {\(\mach,(\domMap,\target::\rts) \stepsto_C
                \pop{\domMap}{\depth},\rts\)}

\judgmentthree[ReturnRec]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \_,\rts'\)}
              {\(\depth = |\rts'|\)}
              {\(\mach,(\domMap,\_::\rts) \stepsto_C
                \pop{\domMap}{\depth},\rts'\)}

@@

\definition Machine state pairs \(\mach,\mach'\) and \(\nach,\nach'\) are {\em synched}
if for all components \(\component\) such that \(\mach ~ \component \not = \mach' ~ \component\) or
\(\nach ~ \component \not = \nach' ~ \component\), \(\mach' ~ \component = \nach' ~ \component\).
This is written \(\mach,\mach' \diamond \nach,\nach'\).

\definition A pair of traces \(\machT\) and \(\nachT\) are {\em in lockstep} if their adjacent pairs
are synched, written as a coinductive relation \(\machT \doteq \nachT\):

@@

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \depth')\) hold for
\(\depth' \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\depth)\) and
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component \not = \outside\).
\(\MPCT\) corresponds to the trace of a subroutine from its call to its return.
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).

\subsection{Stack Safety with Sharing}

Next we introduce sharing. We will need to extend the set of annotations to include
sharing and passing, and now the code map may map a single instruction to multiple
annotations, because in some calling conventions a single instruction might carry
meaning as both a call and a pass. But we will never have a single instruction annotated
as both a call and a return.

\[\ann \in \ANNS ::= \callmap + \retmap + \sharemap(P \subseteq \MACHS \times \COMPONENTS) +
\passmap(P \subseteq \MACHS \times \COMPONENTS)\]

And we extend the set of domains to include shared and passed components, the latter of
which are labeled with the depth of the caller that has passed them.

\[\stackDom \in \STKDOMS ::= \outside + \unsealed + \shared{\depth} + \sealed{\depth} + \passed{\depth}\]
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
\times (\depth \in \mathbb{N}) \]

What it means to push the stack is similar to above, but two details are worth noting.
First, shared and passed components are not sealed by the sealing convention, and second,
anything not touched by the sealing convention must be unsealed. Sharing and passing cannot
apply to memory the callee could otherwise use.

\[
(\push{\domMap}{\depth}{\components}) ~ \component =
\begin{cases}
  \sealed{\depth} & \text{if } \domMap ~ \component = \unsealed
                    \text{ and } \component \in \components \\
  \domMap ~ \component & \text{else if } \component \in \components \\
  \unsealed & \text{else} \\
\end{cases}
\]

Popping is simpler, but note that while passed components are unsealed on return to their
passer, shared ones are unsealed on return {\em from} their sharer - on deallocation,
in other words.

\[
(\pop{\domMap}{\depth}) ~ \component =
\begin{cases}
  \unsealed & \text{if } \domMap ~ \component = \sealed{\depth-1}
              \text{ or } \domMap ~ \component = \passed{\depth-1}
              \text{ or } \domMap ~ \component = \shared{\depth} \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]

Finally we introduce a more direct update. If \(P\) is a relation between machine states and
components, we write \(\domMap[P ~ \mach \mapsto \stackDom]\) to say \(\domMap\) updated
so that each component \(\component\) where \(P ~ \mach ~ \component\) holds is mapped to
\(\stackDom\).

Now we can inductively define the context update function; as these could be ambiguous assume that
they apply in the order presented.

\begin{center}
  \judgment{\(\mach,\context,\anns \stepstocon (\domMap,\depth)\)}
           {\(\mach,\context,(\{\callmap\} \cup \anns) \stepstocon
             (\push{\domMap}{\depth}{\sealcon ~ \mach},\depth+1)\)}
  \judgment{\(\mach,\context,\anns \stepstocon (\domMap,\depth)\)}
           {\(\mach,\context,(\{\retmap\} \cup \anns) \stepstocon
             \mach',(\pop{\domMap}{\depth},\depth-1)\)}
  \judgment{\(\mach,\context,\anns \stepstocon (\domMap,\depth)\)}
           {\(\mach,\context,(\{\passmap ~ P\} \cup \anns) \stepstocon
             \domMap[P ~ \mach \mapsto \passed{\depth}], \depth)\)}
  \judgment{\(\mach,\context,\anns \stepstocon (\domMap,\depth)\)}
           {\(\mach,\context,(\{\sharemap ~ P\} \cup \anns) \stepstocon
             \domMap[P ~ \mach \mapsto \shared{\depth}], \depth)\)}
  \judgment{}
           {\(\mach,\context,\_ \stepstocon \context\)}
\end{center}

\definition Let \(\MPCT\) be a reachable trace segment of the form
\(\mpcstatename ~ \mpcstatename'\), where \(\pi_\context(\mpcstatename) = (\domMap,\depth)\).
Let \(\components\) be the set of components \(\component\) such that either
\(\domMap ~ \component = \sealed{\_}\) or \(\domMap ~ \component = \passed{\depth'}\) for
some depth \(\depth' < \depth-1\). If any such \(\MPCT\) obeys trace integrity with respect
to \(\components\), then the system enjoys {\em ultra-eager confidentiality} in the sharing
model.

\definition Let \(\MPCT \langle f \rangle\) be a reachable trace segment where \(f\) holds
on contexts whose depth is less than or equal to some \(\depth\). Let \(\head(\MPCT) =
\mpcstate{\mach}{\pol}{(\domMap,\depth')}\) and \(\components\) be the set of components
\(\component\) such that either \(\domMap ~ \component = \sealed{\_}\) or
\(\domMap ~ \component = \passed{\depth''}\) for some depth \(\depth'' < \depth'-1\).
Then the system enjoys {\em eager integrity} in the sharing model if \(\MPCT\) obeys
trace integrity with respect to \(\components\).

\definition Let \(\MPCT \langle f \rangle\) be a reachable trace segment where \(f\) holds
on contexts whose depth is less than or equal to some \(\depth\). Let \(\head(\MPCT) =
\mpcstate{\mach}{\pol}{(\domMap,\depth')}\) and \(\components\) be the set of components
\(\component\) such that either \(\domMap ~ \component = \outside\) or
\(\domMap ~ \component = \shared{\_}\). Then the system enjoys {\em eager confidentiality}
in the sharing model if \(\MPCT\) obeys trace confidentiality with respect to \(\components\)
and \(f\).

@@

Our final extension to the model is to add coroutines. We assume a very simple model with
a fixed number of coroutines, each with its own stack.
Stack identifiers are drawn from a set \(\STACKS\), and there is a static partial map
\(\stackof\) from addresses to stack ids. The ``active stack'' -- the stack belonging to the
currently executing coroutine -- in any given machine state is \(\stackof(\mach ~ \SP)\).
We extend the set of possible annotations with a yield.

\[\ann \in \ANNS ::= \callmap + \retmap + \yieldmap +
\sharemap(P \subseteq \MACHS \times \COMPONENTS) +
\passmap(P \subseteq \MACHS \times \COMPONENTS)\]

We use the same domain model as above, but instead of keeping track of a single depth
we use a map from stacks to their depths.

\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS) \times
(\depthMap \in \STACKS \rightarrow \mathbb{N})\]

\subsection{Local State Encapsulation}

\definition A system enjoys {\em local state encapsulation} if it enjoys eager integrity and
eager confidentiality.

\definition A system enjoys {\em lazy local state encapsulation} if it enjoys lazy integrity
and eager confidentiality.

We do not give a confidentiality equivalent to lazy integrity, because the family of lazy
enforcement mechanisms that we consider under the HOPE system in fact enforce eager confidentiality.
A policy based on taint-tracking might require such a lazy confidentiality, and it would be constructed
by replacing the ``same-difference'' condition with one that requires any differences to produce
observationally equivalent states. But for our purposes it is irrelevant.

\section{Well-bracketed Control Flow}
\label{sec:wbcf}

Both the integrity and confidentiality components of local state
encapsulation concern themselves only with the accessibility of data,
and may still hold on a wide range of programs that violate expected
control flow. The archetypal example of this is the {\em awkward example},
in which an adversarial callee stores a return address and returns to it
on a subsequent call, thus violating the expected control flow of the
caller without actually violating the caller's integrity. But it also
encompasses simpler violations, such as a function bypassing a password
check by jumping (or returning) in the middle of a block of code.
%
Stack safety enforcement mechanisms like \citet{Skorstengaard+19}
usually aim to prevent such unwanted flows: every jump between
functions should either be a call or a return, and each return should
be to the instruction after its corresponding call.

To formally capture this aspect of stack safety, we introduce some more
security properties. {\em Control separation} restricts transitions between
functions to follow the interfaces set out by call, return, and yield, forming
a foundation for all of the other properties that rely on those interfaces for
meaning. {\em Entry integrity} ensures the validity of call targets,
{\em return integrity} ensures that of return targets, and
{\em yield-back integrity} ensures that of yield targets.

Recall that our properties use a compiler-derived code-map determine
which addresses are instructions and which functions they belong to, as well
as annotating them as calls, returns, and yields, as well as sharing information.
We now extend it with an annotation for valid entry points:
\[\ann \in \ANNS ::= \callmap + \retmap + \yieldmap +  \entmap + 
\sharemap(P \subseteq \MACHS \times \COMPONENTS) +
\passmap(P \subseteq \MACHS \times \COMPONENTS)\]

\definition%{Control Separation}

Let \(\mpcstatename\) be a reachable state whose program counter points to code in
function \(\funid\), and \(\mpcstatename \stepstopol \mpcstatename'\) where
\(\mpcstatename'\) is state whose program counter points to a different function
\(\funid'\). A system enjoys {\em control separation} when all such \(\mpcstatename\)
are annotated \(\callmap\), \(\retmap\), or \(\yieldmap\).

\definition%{Entry Integrity}
A system enjoys {\em entry integrity} when, for any reachable \(\mpcstatename\) and
\(\mpcstatename'\) such that \(\mpcstatename\) is annotated \(\callmap\) and
\(\mpcstatename \stepstopol \mpcstatename'\), \(\mpcstatename'\) is annotated \(\entmap\).

\definition%{Return Integrity}
A system enjoys {\em return integrity}... [this one needs to talk about context.]

\definition%{Yield-back Integrity}
A system enjoys {\em yield-back integrity}... [same.]

\definition% {Well-Bracketed Control Flow}
The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system with all three
properties (with respect to a function map, call map, return map,
and entry map) is said to enjoy
{\em well-bracketed control flow} (with respect to those maps).

@@

\paragraph{Rolling Back to Idealized State}

Observable integrity weakens eager integrity by allowing a returned
state to differ from its call state at high integrity components,
provided that the differences do not change the observable behavior of
the rest of the program. The challenge here is to define what constitutes
a change in behavior. We construct an idealized return state that
contains only the changes that the caller was allowed to make, and use
the trace from that state as a baseline against which the real trace
will be compared.

      \definition

      Given a contour, a call state, and a returned state, we define a
      {\em rollback} function \(\mathit{roll} \in \CONTOURS \times \MACHS \times
      \MACHS \rightarrow \MACHS\). The rollback returns a state that matches
      the call state on those components that are high integrity in its
      contour, and matches the return state on low integrity components:
      \[\mathit{roll}(\contour,\mach_e,\mach_r)(\component) =
      \begin{cases}
        \mach_e(\component) & \text{if } \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \text{if } \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      If \(\mach_e\) is an entry to a call with contour \(\contour\)
      and \(\mach_r\) its return, the result of
      \(\mathit{roll}(\contour,\mach_e,\mach_r)\) agrees with the
      entry \(\mach_e\) on every component the callee should not
      change, and with the actual return \(\mach_r\) on those
      components that it is permitted to change.  So the observable
      behavior that follows is the idealized behavior to which we
      compare the trace from \(\mach_r\).

      Now we can define a version of trace integrity that compares the trace
      from a returned state to that from its idealized counterpart.

    \definition%{Observable Trace Integrity}

      A trace enjoys {\em observable trace integrity} with respect to
      some contour \(\contour\) if the trace induced by its final
      state (if any) has observable behavior that prefixes that of its
      idealized version (to account for premature halts due to policy
      violations):

      \[\begin{split}
        \propdef{ObsTraceInt} ~ \contour ~ \MPT \ \ \triangleq \ \
        & \head(\MPT) = \mpostate{\mach_e}{\_}{\_} ~ \land ~
          \last(\MPT) = \mpostate{\mach_r}{\pol_r}{\_} ~ \land \\
        & \mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT' ~ \land ~
          \mathit{roll}(\contour,\mach_e,\mach_r) \hookrightarrow \machT'
          \Rightarrow \\
        & \pi_o(\MPT') \lesssim_O \pi_o(\machT')
      \end{split}\]

%    \begin{figure}
%      \integritylazyexample
%      \caption{Rolling back from Figure \ref{fig:intex}.}
        %\apt{But at 27, $[\rsp]$ contains 0, not 18, because of the change at 44. Could just fix diagram, but this complicates story.}}
%      \label{fig:intlex}
%    \end{figure}

    For our example, we return to the violation of trace integrity in
    \cref{fig:intex}, in which {\tt g} has written to {\tt z} and returned.
    Whether observable integrity holds depends on the continuing trace, shown
    in \cref{fig:intlex}. Above, we have the final state of \(\MPT\),
    \(\mach_r\), and the rolled-back state, \(\mach_r' =
    \mathit{roll}(\contour,\mach_e,\mach_r)\), in which high integrity
    components are restored to their values as of \(\mach_e\). Specifically,
    address 103 is restored to 0. When instruction 31 prints {\tt z} in the
    trace from \(\mach_r\), it prints 18, but in the trace from \(\mach_r'\)
    it prints 0. Only then is observable trace integrity violated.

    However, consider instead if we modify the original code of \cref{fig:running-trace-b} to insert after instruction 44 a new
    instruction \(44.5: [\rsp-4] \leftarrow 50\), overwriting {\tt w} in
    {\tt f}'s frame. So \(\mach_r'\) maps address 105 to 50, while the
    rolled-back state \(\mach_r'\) maps it to 0. But in the trace from either
    state, instructions 27 and 28 load the return value (18) and store it to
    105, eliminating the only difference. The remainder of the observation
    traces must be identical, so this trace does obey observable trace
    integrity.

    \definition%{Observable Stack Integrity}

      A system enjoys {\em observable stack integrity}, like stack integrity,
      if, for any initial state and each \(n\)-transition from
      \(\mpstate{\mach_c}{\pol_c}\) to \(\mpstate{\mach_e}{\pol_e}\) in its
      induced trace, we take the prefix of the call
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT_{\mathit{call}} ~ | ~ \ret{\mach_c}\)
      and observable trace integrity holds on \(\MPT_{\mathit{call}}\) with
      contour \(\mathit{Cof}(\mach_c,n)\).

@@

      Two of the cases of trace confidentiality (\cref{def:trace-conf}), \(\mathit{InfCase}\)
      and \(\mathit{FailCase}\), are defined solely in terms of
      observation traces. If
      the traces are infinite, they should be similar; if one
      fail-stops, it should be a prefix. Only the
      \(\mathit{ReturnCase}\) checks machine states, because in that
      case the traces could continue, but have been cut off by a
      return. The key to making confidentiality lazy is not to perform that
      check but rather to consider the traces after that return,
      checking only whether they are observationally similar.

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

@@

An initial context \(\context_0 = \domMap_0, []\) where \(\domMap_0\) maps
the stack to \(\unsealed\) and all other addresses and all registers to \(\outside\).

Now we can define the context update relation. Let \(\sealcon\) be the sealing convention
that maps a machine state to a set of components, typically the set of addresses below
the stack pointer. Similarly, \(\retcon ~ \mach ~ \mach'\) will be the return convention
that relates the call state \(\mach\) to return states \(\mach'\) that are valid returns.
The usual return convention is that \(\mach\) and \(\mach'\) agree on the stack pointer,
and \(\mach'\) has its program counter advanced by one instruction from \(\mach\).
Then at each step we update the context according to the context-step function,
\(\stepsto_C\).

The rules for \(\stepsto_C\) are given inductively, and apply in the listed order.
A call simply pushes the return target onto the return stack and seals all components
with the depth of the previous return stack. A return
recursively searches for a valid return target at the next step, and unseals
every component sealed at a depth that it passes.

\judgmentthree[Call]
              {\(\codemap ~ (\mach ~ \PCname) = \callmap\)}
              {\(\components = \sealcon ~ \mach\)}
              {\(\domMap' = \domMap[\components \mapsto \sealed{|\rts|}]\)}
                {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)}

\judgmenttwobr[ReturnFound]
              {\(\codemap ~ (\mach ~ \PCname) = \retmap\)}
              {\(\mach \stepsto \mach' \in \target\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\domMap' = \domMap[\components \mapsto \unsealed]\)}
              {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap',\rts\)}

\judgmenttwobr[ReturnRec]
              {\(\codemap ~ (\mach ~ \PCname) = \retmap\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\components = \{\component | \domMap ~ \component = \sealed{|\rts|}\}\)}
              {\(\domMap'' = \domMap'[\components \mapsto \unsealed]\)}
              {\(\mach,(\domMap,\_::\rts) \stepsto_C \domMap'',\rts'\)}

@@

\definition Machine state pairs \(\mach,\mach'\) and \(\nach,\nach'\) are said to change together
if for all components \(\component\) such that \(\mach ~ \component \not = \mach' ~ \component\) or
\(\nach ~ \component \not = \nach' ~ \component\), \(\mach' ~ \component = \nach' ~ \component\).
This is written \(\mach,\mach' \diamond \nach,\nach'\).

\definition A pair of traces \(\machT\) and \(\nachT\) are {\em in lockstep} if their adjacent pairs
change together, written as a coinductive relation \(\machT \doteq \nachT\):

@@

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \rts)\) hold for
\(|\rts| \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\) and
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component = \outside\).
\(\MPCT\) corresponds to the trace of a subroutine from its call to its return.
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).

\subsection{Stack Safety with Passing}

Next we introduce variable passing. We will need to add extra information to our call
annotations to reflect that they may now pass variables on the stack, and that the locations
of those variables may be dynamic (as in the case of pass-by-reference).
A call annotation now includes a predicate relating machine states to the components
that should be passed -- when passing by value, this will typically give the memory cells
at the appropriate offset from the stack pointer, while passing by reference gives the
addresses of the appropriate variables wherever they happen to be.

\[\ann \in \ANNS ::= \callmap(P \subseteq \MACHS \times \COMPONENTS) + \retmap\]

And we extend the set of domains to include passed components,
which are labeled with the range of depths of the caller that has passed them.

\[\stackDom \in \STKDOMS ::= \outside + \unsealed + \sealed{\depth} + \passed{\depth,\depth'}\]
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
\times (\rts \in \listT (\target \subseteq \MACHS)) \]

We straightforwardly describe how the sealing convention and passing predicate combine to
update a domain map when pushing it, where \(\depth\) is an integer depth.

\[(\mathit{push} ~ \domMap ~ \sealcon ~ P ~ \mach ~ \depth) ~ \component =
\begin{cases}
  \sealed{\depth}              & \text{if } \domMap ~ \component = \unsealed \text{ and }
                                 \sealcon ~ \mach ~ \component \text{ and } \neg P ~ \mach ~ \component \\
  \passed{\depth,\depth+1}     & \text{if } \domMap ~ \component = \unsealed \text{ and }
                                 \sealcon ~ \mach ~ \component \text{ and } P ~ \mach ~ \component \\
  \passed{\depth',\depth+1}    & \text{if } \domMap ~ \component = \passed{\depth',\depth} \text{ and }
                                 \sealcon ~ \mach ~ \component \text{ and } P ~ \mach ~ \component,
                                 \text{ for any } \depth' \\
  \domMap~\component & \text{else} \\
\end{cases}\]

And to pop we just unseal the components at depth \(\depth\):

\[(\mathit{pop} ~ \domMap ~ \depth) ~ \component =
\begin{cases}
  \unsealed                 & \text{if } \domMap ~ \component = \sealed{\depth} \\
  \unsealed                 & \text{if } \domMap ~ \component = \passed{\depth,\depth} \\
  \passed{\depth',\depth-1} & \text{if } \domMap ~ \component = \passed{\depth',\depth}
                              \text{ for any } \depth' < \depth \\
  \domMap~\component        & \text{else} \\
\end{cases}\]

Now we can inductively define the context update function; these again apply in the order
presented.

\judgmenttwo[Call]
            {\(\codemap ~ (\mach ~ \PCname) = \callmap(P)\)}
            {\(\domMap' = \mathit{push} ~ \domMap ~ \sealcon ~ P ~ \mach ~ |\rts|\)}
            {\(\mach,(\domMap,\rts) \stepsto_C \domMap',(\retcon ~ \mach)::\rts\)}

\judgmentthree[ReturnFound]
              {\(\codemap ~ (\mach ~ \PCname) = \retmap\)}
              {\(\mach \stepsto \mach' \in \target\)}
              {\(\domMap' = \mathit{pop} ~ \domMap ~ |\rts|\)}
              {\(\mach,(\domMap,\target::\rts) \stepsto_C \domMap',\rts\)}

\judgmentthree[ReturnRec]
              {\(\codemap ~ (\mach ~ \PCname) = \retmap\)}
              {\(\mach,(\domMap,\rts) \stepsto_C \domMap',\rts'\)}
              {\(\domMap'' = \mathit{pop} ~ \domMap ~ |\rts|\)}
              {\(\mach,(\domMap,\_::\rts) \stepsto_C \domMap'',\rts'\)}

\definition Let \(\mpcstatename\) and \(\mpcstatename'\) be reachable states such that
\(\mpcstatename \stepstocon \mpcstatename'\), and \(\pi_\context(\mpcstatename) = \domMap,\rts\).
Let \(\components\) be the set of components \(\component\) where 
\(\domMap ~ \component = \sealed{\_}\) or \(\passed{\depth,\depth'}\) where \(|\rts| < \depth\)
or \(|\rts| > \depth'\). A system enjoys {\em stepwise stack integrity with passing} if for all
such states, \(\pi_\mach(\mpcstatename) ~ \component = \pi_\mach(\mpcstatename') ~ \component\).

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \rts)\) hold for
\(|\rts| \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \unsealed\) or \(\passed{\depth,\depth'}\) where
\(\depth \leq |\rts| \leq \depth'\) .
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality with passing} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).

@@

Our final extension to the model is to add coroutines. We assume a very simple model with
a fixed number of coroutines, each with its own stack.
Stack identifiers are drawn from a set \(\STACKS\), and there is a static partial map
\(\stackof\) from addresses to stack ids. Note that we now explicitly reference the stack
pointer, using the \(\stackof\) of the stack pointer to determine the target of a yield.
We extend the set of possible annotations with a yield annotation.

\[\ann \in \ANNS ::= \callmap(P \subseteq \MACHS \times \COMPONENTS) + \retmap + \yieldmap\]

The first major difference in this model is the domains. Stack domains are now nested inside
top-level domains, and associated with stack identifiers.
Our context now consists of a domain map, a map from stack identifiers to return target stacks,
an additional map of targets for yields, and a stack identifier of the active stack.
Our yield target map \(\yts\) is a map from stack identifiers to targets.
In a standard system an initial yield target map will map each stack identifier to the
set of all states with their stack pointer at the stack base. When yielding from state \(\mach\),
\(\ycon ~ \mach \subseteq \MACHS\) tells us what yielding back looks like.

\[\stackDom \in \STKDOMS ::= \unsealed + \sealed{\depth} + \passed{\depth-\depth'}\]
\[\topDom \in \TOPDOMS ::= \outside + \instack{\stackid}{\stackDom}\]
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS) \times
(\rtm \in \STACKS \rightarrow \listT ~ \target) \times (\yts \in \STACKS \rightarrow
\target) \times (\stackid \in \STACKS)\]

In our context update rules, calls and returns work the same as in the sharing model,
with domain updates restricted to the top-level domain corresponding to the active stack,
and likewise using the return target stacks. We will omit these rules and focus on the new yield rule.

\judgmentthreebr[Yield]
                {\(\codemap ~ (\mach ~ \PCname) = \yieldmap\)}
                {\(\mach \stepsto \mach'\)}
                {\(\stackid' = \stackof ~ (\mach'~ \rsp)\)}
                {\(\stackid \not = \stackid'\)}
                {\(\yts ~ \stackid'\)}
                {\(\yts' = \yts[\stackid \mapsto \ycon ~ \mach]\)}
                {\(\mach,(\domMap,\rts,\yts,\stackid) \stepsto_C \domMap,\rts,\yts',\stackid'\)}

This calls for some explanation. First, we determine which coroutine we are yielding to by
checking which stack the stack pointer of the next state is pointing to. Then we can only yield
if the next state is a valid yield target for that stack, and we update the yield target for
the yielding stack. So it is once again possible for a coroutine to claim to yield but not
actually change the active stack, with similar effects to when a callee fails to return properly.
Now we can define both stack safety and coroutine safety under this model.

\definition Let \(\mpcstatename\) and \(\mpcstatename'\) be reachable states such that
\(\mpcstatename \stepstocon \mpcstatename'\), and \(\pi_\context(\mpcstatename) = \domMap,\rtm,\yts,\stackid\).
Let \(\components\) be the set of components \(\component\) where 
\(\domMap ~ \component = \instack{\stackid}{\sealed{\_}}\) or \(\instack{\stackid}{\passed{\depth,\depth'}}\)
where \(|\rtm ~ \stackid| < \depth\) or \(|\rtm ~ \stackid| > \depth'\). A system enjoys
{\em stepwise stack integrity} in the coroutine setting if for all
such states, \(\pi_\mach(\mpcstatename) ~ \component = \pi_\mach(\mpcstatename') ~ \component\).

\definition Let \(\mpcstatename\) and \(\mpcstatename'\) be reachable states such that
\(\mpcstatename \stepstocon \mpcstatename'\), and \(\pi_\context(\mpcstatename) = \domMap,\rtm,\yts,\stackid\).
Let \(\components\) be the set of components \(\component\) where 
\(\domMap ~ \component = \instack{\stackid'}{\_}\) where \(\stackid \not = \stackid'\).
A system enjoys {\em stepwise coroutine integrity} in the coroutine setting if for all
such states, \(\pi_\mach(\mpcstatename) ~ \component = \pi_\mach(\mpcstatename') ~ \component\).

\definition Let \(\stackid\) be a stack identifier, \(\depth\) be any depth, and
\(f_\depth ~ \mach ~ (\_, \rtm, \_, \stackid)\) hold for \(|\rtm ~ \stackid| \geq \depth\).
For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rtm,\yts,\stackid)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\unsealed}\) or \(\instack{\stackid}{\passed{\depth,\depth'}}\)
where \(\depth \leq |\rtm ~ \stackid| \leq \depth'\) .
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality} in the coroutine setting if for all
such \(\MPCT\) and \(\NPCT\), \(\MPCT \doteq \NPCT\).

\definition Let \(\stackid\) be a stack identifier, \(\depth\) be any depth, and
\(f_\depth ~ \mach ~ (\_, \rtm, \_, \stackid)\) hold for \(|\rtm ~ \stackid| \geq \depth\).
For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rtm,\yts,\stackid)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\_}\).
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise coroutine confidentiality} in the coroutine setting if for all
such \(\MPCT\) and \(\NPCT\), \(\MPCT \doteq \NPCT\).

\subsection{Well-bracketed Control Flow}
\label{sec:wbcf}

Both the integrity and confidentiality components of stack safety
are reasonable even in programs that violate expected
control flow. But even though stack safety prevents control-flow violations
from being used to gain privileges, it is worth protecting control flow as well.
Indeed, all of the enforcement mechanisms we discuss do preserve well-bracketed
control flow.

When we focus on subroutines, the essence of well-bracketed control flow
is that a caller can expect that if its callee ever returns, it returns
to the caller at the appropriate return target. This is tantamount to saying
that we never ``skip'' a return, or perform a ``false'' one. To formalize this in
the simple model:

\definition A system enjoys {\em well-bracketed control flow} if for all
reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
\(\mpcstatename \stepstocon \mpcstatename'\), if
\(\pi_c(\mpcstatename) = (\_, \_::\rts)\) and \(\pi_m(\mpcstatename)\)
is annotated as a return, then \(\pi_c(\mpcstatename) = (\_, \rts)\).

Extending this idea to coroutines, we use the same notion that there are
no ``false'' yields.

\definition A system enjoys {\em well-structured control flow} if for all
reachable states \(\mpcstatename\) and \(\mpcstatename'\) such that
\(\mpcstatename \stepstocon \mpcstatename'\), if
\(\pi_c(\mpcstatename) = (\_,\_,\_,\stackid)\) and \(\pi_m(\mpcstatename)\)
is annotated as a return, then \(\pi_c(\mpcstatename) = (\_,\_,\_,\stackid')\)
where \(\stackid \not = \stackid'\).

@@

@@
